Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics

### 2020-01-09 ia/ia_vis_3d.tex
0109

\title{Unfolding the City: Spatial Preference Based on Individual Characteristics}

\author{\uppercase{Qi wang}\authorrefmark{1,2}, \uppercase{min lu}\authorrefmark{2,3} and \uppercase{Qingquan Li}\authorrefmark{1,2}}
\address[1]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430072, China}
\address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
\address[3]{School of Architecture and Urban Planning, ShenZhen University, Shenzhen 518060, China}

@@

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual social characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns. Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
\PARstart{T}{he} science fiction \textbf{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people prefer to select different places according to individual characteristics, such as social, economic, educational features. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\cite{pahl1975whose} posed the question "whose city" and interest in understanding the territorial inequalities. Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}. Having a good understanding of relationships between the spatial attractiveness and the characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

In the past decades, the power of visual analytics in exploring spatiotemporal data has been recognized and well developed. Various urban problems are answered, such as traffic jams~\cite{wang2013visual}, interchanging flows in public transportation~\cite{zeng2013visualizing}, etc. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\cite{chen2017map} or topics~\cite{bosch2013scatterblogs2}. Those works essentially contribute in deepening the contextual understanding of moving activity. However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles. One of the main challenges is the sensitivity issue in privacy data. There is still a research gap in exploring the relationship between spatial pattern and social characteristics.

In this work, we contextualize the analysis of citizens' spatial distribution in the backcloth of individual characteristics. With the motivation of fusing the movement data with individuals' profiles in an attempt to ascertain the spatial distribution for groups with different characteristics, we need to get the characterized information of movers. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to count information online. In this work, with a census survey released via social media application, we ran an online demographical collection campaign. Based on the data collected, we developed a visual analytics system to explore where do citizens prefer to go. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the distribution of movements. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method. There are two contributions of this work:

(1) investigate mobility patterns with characteristics, which is a natural step into research of social understanding of the city.

@@

\section{Related Work}
This work concerns the research topic of spatial data visual analytics. Spatiotemporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

@@

\label{sec:concept}
This work was sparked from a meeting with two domain experts who work on human mobility and urban informatics in the geospatial field. The experts pointed out that as big and open data evolved in, the scope of urban research has been lifted from the spatial perspective up to social-spatial perspective. There is a rising research interest in understanding how groups of citizens with certain social characteristics select places during their daily lives. Whether people visit places with preference which are intrinsically affected by their social-economic characteristics? Is there a limitation or probabilities of interaction between different socio-economic groups in public spaces? With the advances of data acquisition and analysis techniques, they demanded to go beyond the conventional static sampled questionnaires, which usually survey visiting preferences. They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive examination of spatial distribution in different contexts of social characteristics.

Thereafter we booted up this project with several rounds of discussions, to frame the research problem with two core contents and the research procedure. The first concepts is \textbf{Social Characteristics}.  Social characteristics of a person or group of citizens  are the descriptors which contribute to the specification of the populations. This work intends to cover the social characteristics from multi-facets, including descriptors such as gender, income, education, etc. The second content is \textbf{Spatial Distribution}. It is reflected by the popularity of a place to be visited.

Motivated by their research interest in understanding the spatial attractiveness with individual social characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.

\section{Data Description}
\label{subsec:pipeline}
Considering there is no existing public dataset could fit our topic well, this work is consolidated with a self-maintained data sourcing. We release an online data census to collect the social characteristics and movement logs of individuals for almost half a year. Then a series of statistical analysis is performed on the collected data for sampling bias checking.

\subsection{Online Census}

The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data by apps within the phones. Complementary to the conventional census, it brings the benefit of convenient collections without much manpower and precise spatial locations by GPS instead of semantic description. Meanwhile, it is possible to collective the movement in human inactive time, such as the mid-night.

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, the most widely used social media mobile application. Fig. \ref{fig:app} shows the data collecting interfaces. For privacy issue, all detailed personal information are desensitized to categorical levels. Considering the main aim on the relationship between spatial distribution of movements and individuals' characteristics, there are two crucial contents to be collected:

\textbf{Individual Characteristics} Fig. \ref{fig:data_over} lists the eight domains, including social, economic and demographic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires the information of start/end location, start/end time, traveling purpose. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

@@

Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals (48\% females and 52\% males) participated in the census and 229,155 trips were collected. Each volunteer contributed 11 trips average.

@@

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their profile  and movements.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

Fig. \ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of ages, dominating between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate.

Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200,000. Individuals with higher salary are also reached in our census.

@@

Fig. \ref{fig:data_geometry} shows the basic statistics related to movements. In Fig. ~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life. There are obvious morning and late afternoon peaks. Fig. ~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Fig. ~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3}
 \caption{Statistics of Trips: (a) start time of trips; (b) purpose of trips; (c) distribution of origins/destinations }
 \label{fig:data_geometry}
\end{figure}

Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population.

@@

\begin{itemize}
\item \textbf{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textbf{Task 2: Explore the mobility distribution of a group}: to explore where, how and why an interested group go in the city.
\item \textbf{Task 3: Compare mobility distribution among multiple groups}: to know the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual characteristics.
\end{itemize}

@@

With these three tasks, we derive following design considerations:

\begin{itemize}
\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.
\item \textbf{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
\item \textbf{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
\item \textbf{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information.
\item \textbf{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textbf{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
\end{itemize}

@@

With those design considerations, we develop a visual analytics system as Fig. \ref{fig:teaser} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

@@

Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}). The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point. In the cases where occlusion is inevitable, an interaction named as \textbf{Detail Slicing} is developed, as Fig. ~\ref{fig:2.5D}(b) shows. Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting. The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.

@@

% \lmc{Add a section to introduce the domain experts' feedback}
% \lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}

We ran an interview with the two domain experts, to ask about their feedback on the designed system. Overall, the two domain experts praised high for the full walk-through from data collection to analysis, towards the research problem of spatial preference with social individuals. They also appreciated the overall design of a visual analytic system and the finding cases. Specifically, they pointed out what they like and also to be improved.

Expert A expressed her like in the data-driven profile visualization. She commented that ``it takes little effort to learn how to read it, which really taps into my daily experience.''. Expert B also commented the data-driven profile visualization provides an intuitive representation of individuals, though sometimes it is cumbersome to recognize each of them when there are too many. But he said the combination usage of profile and t-SNE is very efficient, which enables him to quickly identify individuals from the mass. Both two experts spoke highly about dynamic identifying groups of interest and on-the-fly analysis of the spatial preference. Expert A commented that ``the visual analytic system allows me to try any group of interest''. Expert B like the cross-filtering interactions across multiple views.  For spatial visualization, both two experts thought our solution, 2.5D visualization is a grid-based spatial visualization is a fancy design choice. With detail slicing function, not only the overview of the spatial distribution, but also the inner details of each TAZ could be filtered out and check directly.

\section{Conclusion}
\label{sec:conclusion}
This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics. Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which is rarely touched by previous geo-tagged social media visual analytics. The design of the visual analytic system is driven by three tasks about individuals and mobility patterns. Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals. Its effectiveness in identifying similar or abnormal individuals from the mass has been demonstrated. The design of 2.5D spatial visualization continues the exploration of the typical research problem how to visualize spatial information and abstract information together. Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.
Our current research focuses on fundamental facets of the spatial preference and doesn’t draw a strong conclusion on the correlation between movements and individual characteristics. In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc.

>>>>

\title{Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics}

\author{\uppercase{Qi wang}\authorrefmark{1,2}, \uppercase{min lu}\authorrefmark{2,3} and \uppercase{Qingquan Li}\authorrefmark{1,2}}
\address[1]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430072, China}
\address[2]{Shenzhen Key Laboratory of Spatial Smart Sensing and Services, Shenzhen University, Shenzhen 518060, China}
\address[3]{School of Architecture and Urban Planning, Shenzhen University, Shenzhen 518060, China}

@@

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual demographic characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse spatial preferences. Different from the well study of anonymous travel behaviors, the daily movement of characterized individuals, is less studied due to the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we design a visual analytic system to investigate the spatial preference to groups by specifying demographic characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
\PARstart{T}{he} science fiction \textbf{Folding Beijing}~\cite{hao2016_foldingbeijing} depicts a world where three social classes of people live in independent spatiotemporal patterns, though sharing the same earth surface. This is an artistic metaphor for one potential fact that people prefer to select different places to live according to individual characteristics, especially personal demographic characteristics. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\cite{pahl1975whose} posed the question "whose city" and interest in understanding the territorial inequalities. Contemporary contestation also continually raises the banner "The City Belongs to All!"~\cite{Mayer2017_whosecity}. Some approaches have been to discuss spatial distribution~\cite{RN909}, spatial interaction~\cite{RN1692} and place attractiveness~\cite{retailcity}. However, lacking of movers' characteristics, they almost only analyzed from the spatial perspective, and individual characteristic factors were not put into the context of the problems. It is required to explore the relationship between spatial preference and individual demographic characteristics for better region utilization, diversity mix-up, and opportunity promotion.

Due to the multidimensional nature of demographic characteristics and spatial diversity of movements, it is challenging to explore, analysis and express the relationship between them. In the past decades, the power of visual analytics on urban problems has been recognized and well developed~\cite{wang2013visual, zeng2013visualizing}. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\cite{chen2017map} or topics~\cite{bosch2013scatterblogs2}. Those works essentially contribute on deepening the contextual understanding of moving activity. \colorbox{yellow}{However, they rarely combine the movement analysis with individuals' characteristics because which cannot be fully inferred from social media profiles. One of the main challenges is the sensitivity issue in privacy data.}
The question of how to intuitively discover the relationship between spatial preference and multidimensional characteristics is worthy of further investigation.

In this work, we contextualize the analysis of citizens' spatial preference in the backcloth of individual demographic characteristics. With the motivation of it, we need to obtain the demographic characteristics of individuals and their daily movements. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to collect information online. In this work, we ran an online demographical collection campaign released via a social media application. Based on the data collected, we developed a visual analytics system to explore where do specified charactered citizens prefer to go. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the spatial distribution of movements. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the power of our method. There are two contributions of this work:

(1) investigate spatial preference with individual demographic characteristics, which is a natural step into research of social understanding of the city.

@@

\section{Related Work}
This work concerns the research topic of spatial data visual analytics. Lots of related work focus on the spatiotemporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual demographic characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

@@

\label{sec:concept}
This work was sparked from a meeting with two domain experts who work on human mobility and urban informatics in the geospatial field. The experts pointed out that as big and open data evolved in, the scope of urban research has been lifted from the spatial perspective up to social-spatial perspective. There is a rising research interest in understanding how categories of citizens with certain demographic characteristics visit places during their daily lives. Whether people select places with preference which are intrinsically affected by their social-economic characteristics? Is there a limitation or probabilities of interaction between different socio-economic groups in public space? With the advances of data acquisition and analysis techniques, they demanded to go beyond the conventional static sampled questionnaires, which usually survey visiting preferences. They sought for the possibility in revealing the spatial distribution in real-world visiting logs and urged to have a dynamic system which supports the interactive exploration of spatial preference in different contexts of demographic characteristics.

Thereafter we booted up this project with several rounds of discussions, to frame the research problem with two core contents and the research procedure. The first content is \textbf{demographic characteristics}. Demographic characteristics of a person or a group of individuals are the descriptors which contribute to the specification of the populations. This work intends to cover the characteristics from multi-facets, including descriptors such as gender, income, education, etc. The second content is \textbf{spatial preference}. It is reflected by the popularity of a place to be visited.

Motivated by their research interest in understanding the spatial preference with individual demographic characteristics, this work goes through a procedure consists of two stages, i.e., data collection and basic reviewing, visual analytics design iteration with experts' feedback.

\section{Data Description}
\label{subsec:pipeline}
Considering there is no existing public dataset could fit our topic well, this work is consolidated with a self-maintained data sourcing. We release an online information survey to collect the demographic characteristics and movement logs of individuals for almost half a year. Then a series of statistical analysis is performed on the collected data for sampling bias checking.

\subsection{Online Survey}

The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data by apps within the phones. Complementary to the conventional survey, it brings the benefit of convenience without much manpower and precise spatial locations by GPS instead of semantic description.

In this work, we perform the survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, the most widely used social media mobile application in China. Fig. \ref{fig:app} shows \colorbox{yellow}{the interfaces of survey app.} For privacy issue, all detailed personal information are desensitized to categorical levels. Considering the main aim on the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:

\textbf{Demographic Characteristics} Fig. \ref{fig:data_over} lists the eight domains to give a generalized description of the individuals. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires the information of start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

@@

Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected. \colorbox{yellow}{Each volunteer contributed 11 trips average.}

@@

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

Fig. \ref{fig:data_age_edu} gives the distribution of gender, age and education over the population. For participated citizens, 48\% of them are female and 52\% are male. It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, dominating between 18 and 45. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate. Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. \colorbox{yellow}{Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.} The majority get paid below 200,000. Citizens with higher salary are also reached in our census.

@@

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. \colorbox{yellow}{Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of trip quantity of each citizen. It has a heavy-tail trait, which follows the law of most human-related statistics}. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3}
 \caption{Statistics of Trips: (a) distribution of trip quantity of each citizen; (b) start time of trips; (c) purpose of trips; (d) distribution of origins/destinations. }
 \label{fig:data_geometry}
\end{figure}

Due to lacking of governmental statistics, we cannot verify all characteristics and movements collected are consistent with all the citizens in Shenzhen. From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population.

@@

\begin{itemize}
\item \textbf{Task 1: Identify the group with specific individual demographic characteristics}: to get groups of people with common or similar attributes, to explore the correlation among individual characteristics.
\item \textbf{Task 2: Explore the spatial preference of a group}: to explore where, how and why an interested group go in the city.
\item \textbf{Task 3: Compare spatial preference among multiple groups}: to express the similarities and differences between different groups in their spatial preferences, to investigate the relationship between movement and individual demographic characteristics.
\end{itemize}

@@

With three tasks above, we derive following design considerations:

\begin{itemize}
\item \textbf{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of end-users' daily experience in sensing individuals' demographic characteristics to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.
\item \textbf{Good overview of the multivariate individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore.
\item \textbf{Effective multivariable cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straight-forward way for easy filtering by the eight criteria.
\item \textbf{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information.
\item \textbf{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textbf{Task 3}, the system should maintain flexible interactions which allow the end-users to explore freely.
\end{itemize}

@@

With all the design considerations, we develop a visual analytics system as Fig. \ref{fig:teaser} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the specified group of individuals, its moving-related information is visualized and explored in a 2.5D spatiotemporal view.

@@

Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}). The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which is continuously flexible that users can find a suitable observing point. In the cases where occlusion is inevitable, a 2D view for overview and an interaction, namely, Detail Slicing, are developed, \colorbox{yellow}{as Fig. ~\ref{fig:2.5D}(b) and (c) shows. Overview view shows all TAZs in the form of 2D plane.} It is for quickly sensing the distribution of the whole city. Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting. The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.

@@

We ran an interview with the two domain experts, to ask about their feedbacks on the designed system. Overall, the two domain experts praised high for the full walk-through from data collection to analysis, towards the research problem of spatial preference with demographic characteristics. They also appreciated the overall design of a visual analytic system and the finding cases. Specifically, they pointed out what they like and also to be improved.

Expert A expressed her like in the data-driven profile visualization. She commented that ``it takes little effort to learn how to read it, which really taps into my daily experience.''. Expert B also commented the data-driven profile visualization provides an intuitive representation of individuals, though sometimes it is cumbersome to recognize each of them when there are too many. But he said the combination usage of profile and t-SNE is very efficient, which enables him to quickly identify individuals from the mass. Both two experts spoke highly about dynamic identifying groups of interest and on-the-fly analysis of the spatial preference. Expert A commented that ``the visual analytic system allows me to try any group of interest''. Expert B like the cross-filtering interactions across multiple views.  For spatial visualization, both two experts thought our solution, 2.5D visualization is a grid-based spatial visualization is a fancy design choice. With detail slicing function, not only the overview of the spatial preference, but also the inner details of each TAZ could be filtered out and check directly.

\section{Conclusion}
\label{sec:conclusion}
This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of spatial preference with individual demographic characteristics. Considering the irresistible trend in mixing demographic data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals’ characteristics, which is rarely touched by previous geo-tagged social media visual analytics. The design of the visual analytic system is driven by three tasks about individuals and mobility patterns. Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals. Its effectiveness in identifying similar or abnormal individuals from the mass has been demonstrated. The design of 2.5D spatial visualization continues the exploration of the typical research problem how to visualize spatial information and abstract information together. Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.
Our current research focuses on fundamental facets of the spatial preference and doesn’t draw a strong conclusion on the correlation between movements and individual characteristics. In next step, more delicate algorithms will be involved to extract high-level spatial preference, such as the frequent visiting sequence of an individual group, etc.
